HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

Perhaps more importantly, references are often not created by translating the source
sentences. In some cases, the manual translation was reversed\oa{what does that mean?},
and in others the ``source'' and ``reference'' are actually independent translations
from a third language. ``References'' can thus easily contain information
that does not appear in the ``source''.

@@

% \subsection{ to be removed}
% 
% In the *MEANT papers they mainly test by either
% A) correlating the metric to ranking judgements; or
% B) using automated versions of the metric for tuning MT systems
% 
% I think neither is particularly convincing, but I'm not sure at the moment what we replace them with. Dekai also made a claim about the *MEANT metrics being "interpretable" in the sense that they could guide you towards semantic errors that the MT system may be making, however I don't recall seeing this done in his papers. 
% 
% By the claim that HMEANT explains things, Dekai probably means that the score is decomposable, but so is UCCA-Eval and even BLEU. And UCCA-Eval has one benefit over HMEANT: it points to words in the MT output that are aligned with something but do not convey the meaning well (and we know which part of the source meaning). Pure HMEANT might say only that some part of the MT output has no clear frames whatsover (and we do not know which part of the source/reference, unless we add the word alignments).
% 
%

>>>>

Perhaps more importantly, references are often not created by translating the source
sentences. In some cases, the manual translation was actually carried out in the
other direction, from ``reference'' to ``source''
and in others the ``source'' and ``reference'' are independent translations
from a third language. ``References'' can thus easily contain information
that does not appear in the ``source''.

@@

\oa{I would consider adding further examples from the Google Doc. For instnace ``your risk of falling'' -- ``Ihr Risiko'' or
  ``Two {\bf review} authors assessed the studies independently and extracted outcome data'' -- ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf \"uberpr\"ufen}''}

% \Subsectionngigngig zu  Zu { to be removed}
% 
% In the *MEANT papers they mainly test by either
% A) correlating the metric to ranking judgements; or
% B) using automated versions of the metric for tuning MT systems
% 
% I think neither is particularly convincing, but I'm not sure at the moment what we replace them with. Dekai also made a claim about the *MEANT metrics being "interpretable" in the sense that they could guide you towards semantic errors that the MT system may be making, however I don't recall seeing this done in his papers. 
% 
% By the claim that HMEANT explains things, Dekai probably means that the score is decomposable, but so is UCCA-Eval and even BLEU. And UCCA-Eval has one benefit over HMEANT: it points to words in the MT output that are aligned with something but do not convey the meaning well (and we know which part of the source meaning). Pure HMEANT might say only that some part of the MT output has no clear frames whatsover (and we do not know which part of the source/reference, unless we add the word alignments).
% 
%
